GPU-friendly Stroke Expansion

### 2024-04-29 paper.tex
Fix typos; add a keywords section with TODO

@@

The error metric for flattening an arc is exact. It always yields the minimum number of subdivisions needed to flatten the curve, and the flattening error is the least possible with given that number of subdivisions. For general curves, an exact error bound is not feasible, and we resort to an approximation. Again the circular arc provides a good example. Applying the small angle approximation $\cos \theta \approx 1 - \theta^2/2$, the approximate distance error is $d = \frac{\kappa s^2}{8n^2}$, and solving for $n$ we get $n = s\sqrt{\frac{\kappa}{8d}}$. Note that this estimate is \emph{conservative,} in that it will always request more subdivision and thus produce a lower error than the exact metric.

@@

An immediate consequence is that flattening an Euler spiral by choosing subdivision points $s_i = a\cdot i^\frac{2}{3}$ produces a near-optimal flattening, as can visually be seen in Figure~\ref{fig:es_flatten}.

@@

The geometry of a stroke outline consists of joins, caps, and the two parallel curves on either side of the input path segments, offset by the half linewidth. The former are not particularly difficult to calculate, but parallel curves of cubic Béziers are notoriously tricky. Analytically, it is a tenth order algebraic curve, which is not particularly feasible to compute directly.

@@

Proposed image: show circular arcs with polar stroking vs near-optimal flattening.

>>>>

\keywords{Vector Graphics, GPU, TODO}

@@

The error metric for flattening an arc is exact. It always yields the minimum number of subdivisions needed to flatten the curve, and the flattening error is the least possible given that number of subdivisions. For general curves, an exact error bound is not feasible, and we resort to an approximation. Again the circular arc provides a good example. Applying the small angle approximation $\cos \theta \approx 1 - \theta^2/2$, the approximate distance error is $d = \frac{\kappa s^2}{8n^2}$, and solving for $n$ we get $n = s\sqrt{\frac{\kappa}{8d}}$. Note that this estimate is \emph{conservative,} in that it will always request more subdivision and thus produce a lower error than the exact metric.

@@

An immediate consequence is that flattening an Euler spiral by choosing subdivision points $s_i = a\cdot i^\frac{2}{3}$ produces a near-optimal flattening, as visualized in Figure~\ref{fig:es_flatten}.

@@

The geometry of a stroke outline consists of joins, caps, and the two parallel curves on either side of the input path segments, offset by the half linewidth. The joins and caps are not particularly difficult to calculate, but parallel curves of cubic Béziers are notoriously tricky. Analytically, it is a tenth order algebraic curve, which is not particularly feasible to compute directly.

@@

TODO: Proposed image: show circular arcs with polar stroking vs near-optimal flattening.
